Differential expression analysis: A pipeline to analyse time-course gene expression data

### 2019-02-20 scripts/02_differential_expression_analysis.Rmd
FIX barplot of California strain was wrong

timely_barplot(K_weekly_de_analysis, time, title="Kawasaki")
timely_barplot(M_weekly_de_analysis, time, title="California")
timely_barplot(VH_weekly_de_analysis, time, title="Vietnam high")
timely_barplot(weekly_de_analysis, time, title="Vietnam low")
```

>>>>

timely_barplot(K_weekly_de_analysis, time, title="Kawasaki")
timely_barplot(C_weekly_de_analysis, time, title="California")
timely_barplot(VH_weekly_de_analysis, time, title="Vietnam high")
timely_barplot(weekly_de_analysis, time, title="Vietnam low")
```
